Article Title

### 2019-09-20 text/03-results.Rmd
Restructuring

```{r cleanup-table}
dt2 <- read.csv("../analyses/cleanup/results/cleanup_table.csv", header=F, stringsAsFactors=F)
dt2$V1 = format_genome(dt2$V1)
kable(dt2, booktabs=TRUE, escape=F, caption = "Number of removed annotations during cleanup.", col.names=c("Genome", "Dataset", "Obsolete Annotations", "Duplicates")) %>%
 kable_styling(latex_options = c("striped")) %>%
 collapse_rows(columns = 1, latex_hline="major")
```

>>>>

```{r cleanup-table}
dt2 <- read.csv("../analyses/cleanup/results/cleanup_table.csv", header=T, stringsAsFactors=F)
dt2$genome = format_genome(dt2$genome)
kable(dt2, booktabs=TRUE, escape=F, caption = "Number of removed annotations during cleanup.", col.names=c("Genome", "Dataset", "Obsolete Annotations", "Duplicates")) %>%
 kable_styling(latex_options = c("striped")) %>%
 collapse_rows(columns = 1, latex_hline="major")
```
